GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-03-20 paper/main.tex
remove the search algorithm in related works

% method
    To address the problem, we propose cooperating three heterogeneous score 
    functions with genetic-based search method, we shall evaulate an architecture 
    from different aspects. More specifically, the first score function is 
    NINASWOT \cite{10.1145/3491396.3506510} as an indicator of the ability 
    to distinguish two images. The second one is the condition number of NTK 
    \cite{https://doi.org/10.48550/arxiv.2102.11535} as score to estimate the 
    trainability of an architecture. The last one is (TBD).

@@

    \section{Related Works}
    In these days, the studies of training-free neural architecture search (NAS) 
    go viral, since the ability to accelerate the procedure for designing a neural 
    network architecture used on specific application, while additionally, 
    training-free NAS cleverly avoid the drawback of long-time training by using 
    various training-free score functions.

    % naswot
    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
    score function without the requirement for training. Here we call it neural 
    architecture search without training (NASWOT) score function. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
    architecture as $f(x_i)$. The activated ReLU units in every layer of the architecture 
    form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix % add figure
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$. 
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow: 
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units between two inputs. An architecture shall learn better 
    when inputs are well separated.

    % ninaswot
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
        \caption{A simple example to illustrate the procedure of noise immunity.}
        \label{fig:ni}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
    Based on the work of Mellor et al., Wu et al. \cite{10.1145/3491396.3506510} 
    found, in some case, an architecture with high score may put different 
    input data, which are originally in the same class, to different classes. 
    To fix this defect, Wu et al. proposed using noise immunity to additionally 
    evaluate an architecture. The score function picks a mini-batch of data, 
    denoted $X$, and then applies Gaussion noise on it, denoted $X'$ and defined 
    by $X'=X+z$ where $z$ is the Gaussion noise. By passing $X$ and $X'$ through 
    the untrained architecture, the sum of the square differences between outputs 
    $O=\begin{matrix}o_1,o_2,\cdots,o_C\end{matrix}$ and 
    $O'=\begin{matrix}o_1',o_2',\cdots,o_C'\end{matrix}$ can be calculated as 
    follows:
    \begin{equation}
        n=-\sum^C_{n=1}(o_i-o_i')^2
    \end{equation}
    where $C$ is the number of classes determined by the input data.
    According to the experiment outcome of Wu et al., noise immunity can separate 
    those are unable to distinguish $X$ and $X'$ from architectures with high NASWOT 
    score, which just complements the NASWOT score funcion.

@@

	% search algorithm
    Another important component of training-free NAS is search algorithm. There're 
    various search algorithms that applied on training-free NAS. The search algorithm 
    that gained much attention in recent years is evolutionary algorithms (EAs) \cite{Liu_2023}.
    In \cite{10.1145/3491396.3506510}, Wu et al. used genetic algorithm (GA), a popular 
    evolutionary algorithm which has great potential to search a vast search space. 
    The NINASWOT score is used as fitness of a chromosome in genetic algorithm. And 
    the tournament selection is used to select an architecture with good NINASWOT score.
    Cavagnero et al. \cite{https://doi.org/10.48550/arxiv.2207.05135} used a custom 
	tournament selection with ageing (REA). Instead of discarding less fitting 
	individuals, REA discards the elder individuals, and thus explore more search 
	space.

    Though the search algorithm is very powerful to search a vast space, the key to the holy 
    grail of training-free NAS is still the training-free score functions. Our work studies 
    the right way to combining the score functions which complements each others, and explore 
    the potential of rank-based GA.

>>>>

% method
    To address the problem, we propose cooperating three heterogeneous score 
    functions with genetic-based search method, which evaulate an architecture 
    from different aspects. More specifically, the first score function is 
    NINASWOT \cite{10.1145/3491396.3506510} as an indicator of the ability 
    to distinguish two images. The second one is the condition number of NTK 
    \cite{https://doi.org/10.48550/arxiv.2102.11535} as score to estimate the 
    trainability of an architecture. The last one is (TBD).

@@

    \section{Related Works}
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
        \caption{A simple example to illustrate the procedure of NASWOT.}
        \label{fig:naswot}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
    In these days, the studies of training-free neural architecture search (NAS) 
    go viral, since the ability to accelerate the procedure for designing a neural 
    network architecture used on specific application, while additionally, 
    training-free NAS cleverly avoid the drawback of long-time training by using 
    various training-free score functions.

    % naswot
    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
    score function without the requirement for training. Here we call it neural 
    architecture search without training (NASWOT) score function. \xfig{fig:naswot} 
	gives a simple example to illustrate the procedure of NASWOT score function. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
    architecture as $f(x_i)$. The activated ReLU units in every layer of the architecture 
    form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix 
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$. 
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow: 
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units between two inputs. An architecture shall learn better 
    when inputs are well separated.

    % ninaswot
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
        \caption{A simple example to illustrate the procedure of noise immunity.}
        \label{fig:ni}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
    Based on the work of Mellor et al., Wu et al. \cite{10.1145/3491396.3506510} 
    found, in some case, an architecture with high score may put different 
    input data, which are originally in the same class, to different classes. 
    To fix this defect, Wu et al. proposed using noise immunity to additionally 
    evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
    noise immunity score evaluate an architecture. The score function picks a 
    mini-batch of data, denoted $X$, and then applies Gaussion noise on it, 
    denoted $X'$ and defined by $X'=X+z$ where $z$ is the Gaussion noise. 
    By passing $X$ and $X'$ through the untrained architecture, the sum of the 
    square differences between outputs 
    $O=\begin{matrix}o_1,o_2,\cdots,o_C\end{matrix}$ and 
    $O'=\begin{matrix}o_1',o_2',\cdots,o_C'\end{matrix}$ can be calculated as 
    follows: 
    \begin{equation}
        n=-\sum^C_{n=1}(o_i-o_i')^2
    \end{equation}
    where $C$ is the number of classes determined by the input data.
    According to the experiment outcome of Wu et al., noise immunity can separate 
    those are unable to distinguish $X$ and $X'$ from architectures with high NASWOT 
    score, which just complements the NASWOT score funcion.

@@

	% synflow?

    % conclusion
